Learning and Reputation under Monopoly and Duopoly: \\A Competing Bandits Approach

### 2018-08-29 paper/competing_bandits.tex
small changes

% Alex' macro
\usepackage{xspace}
\newcommand{\OMIT}[1]{}
\newcommand{\xhdr}[1]{\vspace{1mm} \noindent{\bf #1}}
\newcommand{\ie}{{\em i.e.,~\xspace}}
\newcommand{\eg}{{\em e.g.,~\xspace}}

@@

\noindent \textbf{MAB algorithms} We suppose that firms commit to a learning algorithm from a fixed set of algorithms $\mathcal{A}$. We partition the set of possible learning algorithms into three different types of learning algorithms and restrict $\mathcal{A}$ to contain a representative each algorithm from each class:
\begin{enumerate}
\item "Smart" algorithms that engage in adaptive exploration and combine exploration and exploitation. We consider $Thompson Sampling$ (from hereon $TS$) from this class, which, in a given period, will pull an arm according to the probability that that arm is "optimal" in the sense of having the highest mean reward \cite{agrawal2012analysis}.
\item "Naive" algorithms that engage in non-adaptive exploration algorithms and separate exploration and exploitation. We consider $Dynamic$ $\epsilon$-$greedy$ (from hereon $DEG$) from this class, which, in a given period, pulls the arms with the highest posterior mean for $1 - \epsilon$ probability and selects a random arm with $\epsilon$ probability. For our experiments we keep $\epsilon = 0.05$ fixed.
\item Greedy / myopic algorithms that engage in no purposeful exploration and take the best short-sighted action. We consider $DynamicGreedy$ (from hereon $DG$) from this class, which, in a given period, pulls the arm with the highest posterior mean.
\end{enumerate}

In the standard multi-armed bandit problem it is known that $TS > DEG > DG$ in terms of maximizing cumulative reward over a sufficiently large time horizon. The primary question that we want to understand is when, in competition, are the firms incentivized to adopt the "better" algorithms?

@@

We evaluate the performance of the different learning algorithms on the bandit priors we consider in isolation. There are two reasons why this is important to consider. First, we want to confirm that the reputation ordering of the algorithms is what we would expect according to the multi-armed bandit literature where, according to the mean reputation, $TS > DEG > DG$ for sufficiently large $t$. Second, we want to better understand what statistics of the priors we can look at in isolation in order to help us predict and understand what to expect in the competition game.

@@

Is looking at the mean performance of between two algorithms sufficient for understanding what happens in competition? To answer this, we first look at the entire reputation distribution at $t = 500$ in Figure \ref{rep_dist_nih}. We see that the ``naive" algorithms $DG$ and $DEG$ have a bi-modal reputation distribution whereas $TS$ does not. The intuition for this is that, for Needle In Haystack, $DG$ either finds the best arm or not. If it does, then since it engages in no purposeful exploration it will do better than any algorithm that engages in purposeful exploration over sufficiently many rounds. However, if it does not then it will get stuck on a bad arm and lose to $TS$ or $DEG$. In these cases its reputation may be substantially worse but for the competition game the relative comparison between them is all that matters \footnote{This holds for our model and the decision rule of the agents, though the absolute difference may matter if, for instance, we consider the SoftMax decision rule in \cite{mansour2018competing}}.

To better capture the comparison between two algorithms we explicitly plot the distribution of the reputation difference between $TS$ and $DG$. This figure seems to confirm the intuition noted previously since the reputation distribution has its largest mass around the point just below 0 but it is skewed to the right even as $t$ gets large. Given the skewedness of the distribution, the mean is not a representative statistic of the entire reputation difference distribution. There are alternative statistics that we could consider such as the median or numerically calculating $\Pr(reputation(TS) - reputation(DG)) > 0$ using the estimated density, but instead we define a simple and natural statistic to help us reason about what happens under competition, the \textit{relative reputation proportion}.

\begin{figure}[H]
\caption{Reputation Difference Distribution}
\includegraphics[scale=0.35]{figures/ts_dg_rep_diff_nih}
\label{ts_dg_rep_diff_nih}
\caption*{\tiny{The plots contain a kernel density estimate of the difference in reputation between $TS$ and $DG$ across $t$}}
\end{figure}

@@

\begin{finding}
\textit{Purposeful exploration can lead to relative reputational costs compared to the greedy alternative and this leads to $TS$ doing worse than $DG$ for small time horizons. We observe this under the Uniform and Heavy Tail priors. However, it is not observed under the Needle In Haystack prior}
\end{finding}

The relative reputation statistic corresponds to running the bandit algorithms in isolation on the same instance and with the same realizations for $t$ rounds and then calculating the fraction of simulations at which an agent would select a firm playing $A$ over a firm playing $B$ at time $t$ \footnote{As further motivation for this statistic, one may be interested in if there is ever a case where, for sufficiently large $t$, we observe that $DEG >DG$ or $TS > DG$ according to the mean reputation but $DG > DEG$ or $DG > TS$ according to the relative reputation proportion. In the supplementary material we have results showing that, for Heavy Tail prior with $K=3$ we have that $DEG > DG$ according to the mean reputation but $DG > DEG$ according to the relative reputation proportion. Additionally, these results carry over to the competition game}.

\begin{figure}[ht]
\caption{Relative Reputation Plots}
\includegraphics[scale=0.35]{figures/relative_uniform_annotated_plot}
\includegraphics[scale=0.35]{figures/ts_dg_nih_10_prelim}
\caption*{\tiny{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of both of the algorithms on a given instance and then calculate the proportion of runs where $TS \geq DG$. The shaded area display 95\% confidence intervals.}}
\label{relative_rep_plots}

@@

Figure \ref{relative_rep_plots} shows plots of the relative reputation proportion for $TS$ vs $DG$ on the Uniform and Needle In Haystack prior. For the Uniform prior we see that, in the early rounds, $DG > TS$ for the majority of the simulations but that, eventually, $TS > DG$. The intuition behind this is that, especially since the firms start with no substantive initial information, $TS$ does purposeful exploration in the early rounds in order to acquire information. However, eventually the information acquired from purposeful exploration in the early rounds allows $TS$ to make better decisions and achieve a higher reputation, especially when the instance is ``hard enough" so that $DG$ cannot trivially find the best arm. The early exploration leads to what we define as a \textit{relative reputation cost} and the eventual gain in reputation leads to what we define as a \textit{relative reputation benefit}.

\begin{definition}
\textit{Relative reputation cost and benefit} - the relative reputation loss an algorithm incurs from purposeful exploration compared to the greedy alternative. Here we treat it as an empirical definition based on the relative reputation proportion where the ``cost" regime is when the proportion $< 0.5$ and the ``benefit" regime is when the proportion is $> 0.5$ for the better algorithm. We call the priors where there is an early costly period followed by a later benefit period relative reputation costly priors.
\end{definition}
Is exploration always costly? Figure \ref{relative_rep_plots} also shows that for the Needle In Haystack prior, $TS$ always does relatively better than $DG$. There are two contributing factors to this. First, $TS$ identifies the best arm faster in the Needle In Haystack prior than the Uniform prior so that there is a shorter time horizon where $TS$ needs to engage in purposeful exploration. Second, in the Needle In Haystack prior there are no ``bad" arms as there may be in the Uniform prior since by construction all the arms except one in Needle In Haystack are the same. Thus, when $TS$ pulls a sub-optimal arm relative to its current information, the expected reward is the same as the greedy option that has not identified the best arm. However, with the Uniform prior, it is possible that the sub-optimal arm that is pulled has substantially lower expected reward relative to the greedy option. Thus, only the Uniform and Heavy Tail priors are relative reputation costly priors.

@@

\begin{finding}
\textit{Under the priors that are relative reputation costly and with low warm start, the optimal strategies in the competition game are:
\begin{center}
\textbf{Permanent Monopoly} - $DG$ \\
\textbf{Temporary Monopoly} - $TS$ \\
\textbf{Permanent Duopoly} - $DG$ \\
\end{center}
The conditions on $TS$ being dominant under the temporary monopoly are that the incumbent is a temporary monopoly for sufficiently many periods.
}
\end{finding}

@@

\begin{finding}
\textit{For low warm starts, when exploration is relative reputation costly $DG >TS$ in competition, whereas when exploration is not relative reputation costly $TS > DG$. For sufficiently large warm starts, $TS$ is dominant across all priors.}
\end{finding}

Table \ref{sim_unif} shows the results under the Uniform prior. For the low values of the warm start we can see that $DG > TS$, but that for larger warm starts, $TS > DG$ \footnote{The same results hold for the Heavy Tail prior and are reported in the supplemental material}. Looking at the relative reputation plots in Figure \ref{relative_rep_plots}, we can interpret fixing a warm start $k$ as fixing the starting point on the relative reputation plots. The proportion of first rounds in the competition game that will go to a firm playing alg $A$ over a firm playing alg $B$ will correspond to the relative reputation proportion at time $k$. The intuition for the result in competition aligns with the fact that, for Uniform and Heavy Tail, $TS$ is relative reputation costly compared to $DG$ and so, for low warm starts, $TS$ has not yet recovered from the relative reputation loss due to purposeful exploration and so $DG$ beats $TS$. However, if we move the warm start sufficiently high so that $TS$ moves to the relative reputation benefit regime, $TS > DG$.

However, we do not always see that $DG > TS$ under some warm starts. Table \ref{sim_nih} shows the results for the Needle In Haystack prior where we see that $TS > DG$. This is precisely due to the fact that, under the Needle In Haystack, $TS$ is not relative reputation costly compared to $DG$ and thus we see that $TS > DG$.

@@

\textbf{Temporary Monopoly} We now consider asymmetries in the timing of entry so that one firm enters the market before the other and serves as a monopolist in the periods until the other firm enters. In terms of our model, this corresponds to varying the value of $X$. For this section we report results fixing $k = 20$ and focus on the priors where we observed that, for this warm start, $DG > TS$ \footnote{However, we report the results for the Needle In Haystack prior in the supplementary material. The results are unsurprising, where $TS$ is the dominant strategy for both the entrant and incumbent.}. It seems clear that the temporary monopoly will get a larger market share regardless of what algorithm it plays, but is the incumbent incentivized to commit to $TS$?

\begin{finding}
\textit{Counterintuitively, allowing one firm to be a temporary monopolist for a sufficiently long time will induce that firm to commit to the better learning algorithm, $TS$, even if, under the permanent duopoly, they would commit to $DG$}
\end{finding}

In table \ref{ht_incum} we can see that, for $X = 200$, $TS$ is a dominant strategy for the incumbent and that $DG$ is the dominant strategy for the entrant on the Heavy Tail prior \footnote{The result for the Uniform is the same, though it takes a higher $X$ to induce the incumbent to play $TS$. However, while $DG > TS$ for the entrant, $DG$ does roughly the same as $DEG$ on the Uniform prior. The results are in the supplementary material.}. In the supplementary material we report the same experiment for different values of $X$ and show that our main result that, for sufficiently large $X$, $TS$ is the dominant strategy for the incumbent is robust across priors.

@@

Why do we observe that $TS$ is the dominant strategy for the incumbent whereas in the permanent duopoly experiment we saw that, under the same other conditions, $DG$ was preferred to $TS$? The intuition for this is that competition in the duopoly forces the firms to worry about their reputation which dissuades them from committing to algorithms that involve pure exploration in the early rounds. This intuition is very similar to that observed in the previous section by increasing warm start. One can view allowing one firm to temporarily be a monopolist as temporarily relaxing the "incentive" component of exploration, exploitation, and incentives so that the incumbent firm only faces the classic tradeoff between exploration and exploitation. The incumbent only needs to worry about her reputation after $X$ periods when the entrant comes into the market and again needs to worry about incentivizing agents to select them over their competition. As a result, the incumbent is incentivized to commit to an algorithm that does exploration in the early rounds since she no longer suffers the same relative reputational cost that she would suffer under competition as long as the $X$ is sufficiently large that she can begin to recover the reputational costs of exploration. Thus, counterintuitively, by having one firm be a monopoly and dominate the market, we can incentivize them to play $TS$.

@@

\begin{finding}
\textit{When the incumbent plays $TS$, the data advantage serves as a larger barrier to entry compared to reputation. However, when the incumbent plays $DEG$ or $DG$ there is no substantial difference between the two.}
\end{finding}

Tables \ref{rep_erase} and \ref{info_erase} display the results of these experiments. Maintaining either the data or reputation advantage alone still allows the incumbent to retain a significant portion of the market. The main interesting finding here, which is robust across priors for this parameterization, is that information serves as a larger barrier to entry than reputation when the incumbent plays $TS$. One possible intuition for this is that, for Heavy Tail, the information acquired after the $X$ rounds under $TS$ is sufficient so that it becomes relatively easier for $TS$ to recover the reputation loss compared to the information loss, but since $DEG$ and $DG$ learn slower and they've acquired less information over the $X$ rounds relative to $TS$ there is less of an informational advantage.

Though the setup is purely experimental, it is nonetheless interesting to look at if the same strategies remain best responses in this setting compared to the setting where both data and reputation are retained. We find that the best responses remain the same for the Heavy Tail prior, but for the Uniform prior they change where $TS$ is weakly dominant for the incumbent under the reputation erased treatment but not under the information erased treatment.

>>>>

% Alex' macro
\usepackage{xspace}
\newcommand{\OMIT}[1]{}
\newcommand{\xhdr}[1]{\vspace{1mm} \noindent{\bf #1}}
\newcommand{\ie}{{\em i.e.,~\xspace}}
\newcommand{\eg}{{\em e.g.,~\xspace}}
\newcommand{\TS}{\mathrm{TS}}
\newcommand{\DEG}{\mathrm{DEG}}

@@

\noindent \textbf{MAB algorithms} We suppose that firms commit to a learning algorithm from a fixed set of algorithms $\mathcal{A}$. We partition the set of possible learning algorithms into three different types of learning algorithms and restrict $\mathcal{A}$ to contain a representative each algorithm from each class:
\begin{enumerate}
\item "Smart" algorithms that engage in adaptive exploration and combine exploration and exploitation. We consider Thompson Sampling (from hereon $\TS$) from this class, which, in a given period, will pull an arm according to the probability that that arm is "optimal" in the sense of having the highest mean reward \cite{agrawal2012analysis}.
\item "Naive" algorithms that engage in non-adaptive exploration algorithms and separate exploration and exploitation. We consider $Dynamic$ $\epsilon$-$greedy$ (from hereon $\DEG$) from this class, which, in a given period, pulls the arms with the highest posterior mean for $1 - \epsilon$ probability and selects a random arm with $\epsilon$ probability. For our experiments we keep $\epsilon = 0.05$ fixed.
\item Greedy / myopic algorithms that engage in no purposeful exploration and take the best short-sighted action. We consider $DynamicGreedy$ (from hereon $DG$) from this class, which, in a given period, pulls the arm with the highest posterior mean.
\end{enumerate}

In the standard multi-armed bandit problem it is known that $\TS > \DEG > DG$ in terms of maximizing cumulative reward over a sufficiently large time horizon. The primary question that we want to understand is when, in competition, are the firms incentivized to adopt the "better" algorithms?

@@

We evaluate the performance of the different learning algorithms on the bandit priors we consider in isolation. There are two reasons why this is important to consider. First, we want to confirm that the reputation ordering of the algorithms is what we would expect according to the multi-armed bandit literature where, according to the mean reputation, $\TS > \DEG > DG$ for sufficiently large $t$. Second, we want to better understand what statistics of the priors we can look at in isolation in order to help us predict and understand what to expect in the competition game.

@@

Is looking at the mean performance of between two algorithms sufficient for understanding what happens in competition? To answer this, we first look at the entire reputation distribution at $t = 500$ in Figure \ref{rep_dist_nih}. We see that the ``naive" algorithms $DG$ and $\DEG$ have a bi-modal reputation distribution whereas $\TS$ does not. The intuition for this is that, for Needle In Haystack, $DG$ either finds the best arm or not. If it does, then since it engages in no purposeful exploration it will do better than any algorithm that engages in purposeful exploration over sufficiently many rounds. However, if it does not then it will get stuck on a bad arm and lose to $\TS$ or $\DEG$. In these cases its reputation may be substantially worse but for the competition game the relative comparison between them is all that matters \footnote{This holds for our model and the decision rule of the agents, though the absolute difference may matter if, for instance, we consider the SoftMax decision rule in \cite{mansour2018competing}}.

To better capture the comparison between two algorithms we explicitly plot the distribution of the reputation difference between $\TS$ and $DG$. This figure seems to confirm the intuition noted previously since the reputation distribution has its largest mass around the point just below 0 but it is skewed to the right even as $t$ gets large. Given the skewedness of the distribution, the mean is not a representative statistic of the entire reputation difference distribution. There are alternative statistics that we could consider such as the median or numerically calculating $\Pr(reputation(TS) - reputation(DG)) > 0$ using the estimated density, but instead we define a simple and natural statistic to help us reason about what happens under competition, the \textit{relative reputation proportion}.

\begin{figure}[H]
\caption{Reputation Difference Distribution}
\includegraphics[scale=0.35]{figures/ts_dg_rep_diff_nih}
\label{ts_dg_rep_diff_nih}
\caption*{\tiny{The plots contain a kernel density estimate of the difference in reputation between $\TS$ and $DG$ across $t$}}
\end{figure}

@@

\begin{finding}
\textit{Purposeful exploration can lead to relative reputational costs compared to the greedy alternative and this leads to $\TS$ doing worse than $DG$ for small time horizons. We observe this under the Uniform and Heavy Tail priors. However, it is not observed under the Needle In Haystack prior}
\end{finding}

The relative reputation statistic corresponds to running the bandit algorithms in isolation on the same instance and with the same realizations for $t$ rounds and then calculating the fraction of simulations at which an agent would select a firm playing $A$ over a firm playing $B$ at time $t$ \footnote{As further motivation for this statistic, one may be interested in if there is ever a case where, for sufficiently large $t$, we observe that $\DEG >DG$ or $\TS > DG$ according to the mean reputation but $DG > \DEG$ or $DG > TS$ according to the relative reputation proportion. In the supplementary material we have results showing that, for Heavy Tail prior with $K=3$ we have that $\DEG > DG$ according to the mean reputation but $DG > \DEG$ according to the relative reputation proportion. Additionally, these results carry over to the competition game}.

\begin{figure}[ht]
\caption{Relative Reputation Plots}
\includegraphics[scale=0.35]{figures/relative_uniform_annotated_plot}
\includegraphics[scale=0.35]{figures/ts_dg_nih_10_prelim}
\caption*{\tiny{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of both of the algorithms on a given instance and then calculate the proportion of runs where $\TS \geq DG$. The shaded area display 95\% confidence intervals.}}
\label{relative_rep_plots}

@@

Figure \ref{relative_rep_plots} shows plots of the relative reputation proportion for $\TS$ vs $DG$ on the Uniform and Needle In Haystack prior. For the Uniform prior we see that, in the early rounds, $DG > TS$ for the majority of the simulations but that, eventually, $\TS > DG$. The intuition behind this is that, especially since the firms start with no substantive initial information, $\TS$ does purposeful exploration in the early rounds in order to acquire information. However, eventually the information acquired from purposeful exploration in the early rounds allows $\TS$ to make better decisions and achieve a higher reputation, especially when the instance is ``hard enough" so that $DG$ cannot trivially find the best arm. The early exploration leads to what we define as a \textit{relative reputation cost} and the eventual gain in reputation leads to what we define as a \textit{relative reputation benefit}.

\begin{definition}
\textit{Relative reputation cost and benefit} - the relative reputation loss an algorithm incurs from purposeful exploration compared to the greedy alternative. Here we treat it as an empirical definition based on the relative reputation proportion where the ``cost" regime is when the proportion $< 0.5$ and the ``benefit" regime is when the proportion is $> 0.5$ for the better algorithm. We call the priors where there is an early costly period followed by a later benefit period relative reputation costly priors.
\end{definition}
Is exploration always costly? Figure \ref{relative_rep_plots} also shows that for the Needle In Haystack prior, $\TS$ always does relatively better than $DG$. There are two contributing factors to this. First, $\TS$ identifies the best arm faster in the Needle In Haystack prior than the Uniform prior so that there is a shorter time horizon where $\TS$ needs to engage in purposeful exploration. Second, in the Needle In Haystack prior there are no ``bad" arms as there may be in the Uniform prior since by construction all the arms except one in Needle In Haystack are the same. Thus, when $\TS$ pulls a sub-optimal arm relative to its current information, the expected reward is the same as the greedy option that has not identified the best arm. However, with the Uniform prior, it is possible that the sub-optimal arm that is pulled has substantially lower expected reward relative to the greedy option. Thus, only the Uniform and Heavy Tail priors are relative reputation costly priors.

@@

\begin{finding}
\textit{Under the priors that are relative reputation costly and with low warm start, the optimal strategies in the competition game are:
\begin{center}
\textbf{Permanent Monopoly} - $DG$ \\
\textbf{Temporary Monopoly} - $\TS$ \\
\textbf{Permanent Duopoly} - $DG$ \\
\end{center}
The conditions on $\TS$ being dominant under the temporary monopoly are that the incumbent is a temporary monopoly for sufficiently many periods.
}
\end{finding}

@@

\begin{finding}
\textit{For low warm starts, when exploration is relative reputation costly $DG >TS$ in competition, whereas when exploration is not relative reputation costly $\TS > DG$. For sufficiently large warm starts, $\TS$ is dominant across all priors.}
\end{finding}

Table \ref{sim_unif} shows the results under the Uniform prior. For the low values of the warm start we can see that $DG > TS$, but that for larger warm starts, $\TS > DG$ \footnote{The same results hold for the Heavy Tail prior and are reported in the supplemental material}. Looking at the relative reputation plots in Figure \ref{relative_rep_plots}, we can interpret fixing a warm start $k$ as fixing the starting point on the relative reputation plots. The proportion of first rounds in the competition game that will go to a firm playing alg $A$ over a firm playing alg $B$ will correspond to the relative reputation proportion at time $k$. The intuition for the result in competition aligns with the fact that, for Uniform and Heavy Tail, $\TS$ is relative reputation costly compared to $DG$ and so, for low warm starts, $\TS$ has not yet recovered from the relative reputation loss due to purposeful exploration and so $DG$ beats $\TS$. However, if we move the warm start sufficiently high so that $\TS$ moves to the relative reputation benefit regime, $\TS > DG$.

However, we do not always see that $DG > TS$ under some warm starts. Table \ref{sim_nih} shows the results for the Needle In Haystack prior where we see that $\TS > DG$. This is precisely due to the fact that, under the Needle In Haystack, $\TS$ is not relative reputation costly compared to $DG$ and thus we see that $\TS > DG$.

@@

\textbf{Temporary Monopoly} We now consider asymmetries in the timing of entry so that one firm enters the market before the other and serves as a monopolist in the periods until the other firm enters. In terms of our model, this corresponds to varying the value of $X$. For this section we report results fixing $k = 20$ and focus on the priors where we observed that, for this warm start, $DG > TS$ \footnote{However, we report the results for the Needle In Haystack prior in the supplementary material. The results are unsurprising, where $\TS$ is the dominant strategy for both the entrant and incumbent.}. It seems clear that the temporary monopoly will get a larger market share regardless of what algorithm it plays, but is the incumbent incentivized to commit to $\TS$?

\begin{finding}
\textit{Counterintuitively, allowing one firm to be a temporary monopolist for a sufficiently long time will induce that firm to commit to the better learning algorithm, $\TS$, even if, under the permanent duopoly, they would commit to $DG$}
\end{finding}

In table \ref{ht_incum} we can see that, for $X = 200$, $\TS$ is a dominant strategy for the incumbent and that $DG$ is the dominant strategy for the entrant on the Heavy Tail prior \footnote{The result for the Uniform is the same, though it takes a higher $X$ to induce the incumbent to play $\TS$. However, while $DG > TS$ for the entrant, $DG$ does roughly the same as $\DEG$ on the Uniform prior. The results are in the supplementary material.}. In the supplementary material we report the same experiment for different values of $X$ and show that our main result that, for sufficiently large $X$, $\TS$ is the dominant strategy for the incumbent is robust across priors.

@@

Why do we observe that $\TS$ is the dominant strategy for the incumbent whereas in the permanent duopoly experiment we saw that, under the same other conditions, $DG$ was preferred to $\TS$? The intuition for this is that competition in the duopoly forces the firms to worry about their reputation which dissuades them from committing to algorithms that involve pure exploration in the early rounds. This intuition is very similar to that observed in the previous section by increasing warm start. One can view allowing one firm to temporarily be a monopolist as temporarily relaxing the "incentive" component of exploration, exploitation, and incentives so that the incumbent firm only faces the classic tradeoff between exploration and exploitation. The incumbent only needs to worry about her reputation after $X$ periods when the entrant comes into the market and again needs to worry about incentivizing agents to select them over their competition. As a result, the incumbent is incentivized to commit to an algorithm that does exploration in the early rounds since she no longer suffers the same relative reputational cost that she would suffer under competition as long as the $X$ is sufficiently large that she can begin to recover the reputational costs of exploration. Thus, counterintuitively, by having one firm be a monopoly and dominate the market, we can incentivize them to play $\TS$.

@@

\begin{finding}
\textit{When the incumbent plays $\TS$, the data advantage serves as a larger barrier to entry compared to reputation. However, when the incumbent plays $\DEG$ or $DG$ there is no substantial difference between the two.}
\end{finding}

Tables \ref{rep_erase} and \ref{info_erase} display the results of these experiments. Maintaining either the data or reputation advantage alone still allows the incumbent to retain a significant portion of the market. The main interesting finding here, which is robust across priors for this parameterization, is that information serves as a larger barrier to entry than reputation when the incumbent plays $\TS$. One possible intuition for this is that, for Heavy Tail, the information acquired after the $X$ rounds under $\TS$ is sufficient so that it becomes relatively easier for $\TS$ to recover the reputation loss compared to the information loss, but since $\DEG$ and $DG$ learn slower and they've acquired less information over the $X$ rounds relative to $\TS$ there is less of an informational advantage.

Though the setup is purely experimental, it is nonetheless interesting to look at if the same strategies remain best responses in this setting compared to the setting where both data and reputation are retained. We find that the best responses remain the same for the Heavy Tail prior, but for the Uniform prior they change where $\TS$ is weakly dominant for the incumbent under the reputation erased treatment but not under the information erased treatment.
